\documentclass[letterpaper]{article}


\usepackage{hyperref}
\usepackage{geometry}

\usepackage[T1]{fontenc}
\usepackage{graphicx}

% Set your name here
\def\name{Li Xuanji}


\def\footerlink{}


% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfpagemode = UseNone
}


\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}


\renewcommand{\familydefault}{\sfdefault}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\sffamily\mdseries\Large}
\subsectionfont{\sffamily\mdseries\itshape\large}


% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.


\setlength\parindent{0em}

\begin{document}

\vspace{0.25in}

\begin{minipage}{0.65\linewidth}
\resizebox{0.5\linewidth}{!}{\fontsize{30}{36}\selectfont \name}
\end{minipage}
\begin{minipage}{0.2\linewidth}
  \begin{tabular}{ll}
  1B Honours Computer Science \\
  Student ID: 20591251 \\
  Tel: (+65) 96959264 \\
  Address: Li Xuanji, P.O. Box 16610, East B 123 \\
  Ron Eydt Village, University of Waterloo \\
  Waterloo, Ontario, Canada, N2J 4C1 \\
  \end{tabular}
\end{minipage}

\vspace{2em}


\begin{center}
\section*{Summary of Qualifications}
\end{center}

\begin{itemize}
\setlength\itemsep{0em}
\item Proficience in Python and Javascript developed through internship and side projects.
\item Linux skills developed through installing and configuring Ubuntu for personal use.
\item Experienced with using LaTeX for assignments and academic journal submissions.
\item Familiar with C, C++, Racket Scheme, Haskell, MongoDB, TI-BASIC, Tcl and LaTeX.
\end{itemize}

\vspace{2em}

\begin{center}
\section*{Work Experience}
\end{center}

\subsubsection*{Junior Software Developer - Nugit \hfill May 2014-Present}
\begin{itemize}
\setlength\itemsep{0em}
\item Implemented automated ad performance analysis in Python.
\item Wrote and styled corresponding front-end visualizations.
\item Learned flask, pandas, backbone layoutmanager, svg.js, mongodb.
\item Contributions recognized by CEO as critical to product's successful launch.
\end{itemize}

\subsubsection*{Informatics Coach - NUS High School \hfill Feb-Mar 2014}
\begin{itemize}
\setlength\itemsep{0em}
\item Trained students for National Olympiad in Informatics by running weekly contests.
\item Prepared lessons on basic algorithms and data structures.
\end{itemize}

\vspace{1em}

\begin{center}
\section*{Education}
\end{center}

\subsubsection*{University of Waterloo \hfill Sept 2014}
Candidate for Bachelor of Computer Science.

\subsubsection*{NUS High School \hfill 2006-2011}
Graduated with Honours in Physics, Chemistry, Mathematics and Majors in History.

\subsubsection*{Relevant Courses}
\begin{itemize}
\setlength\itemsep{0em}
\item Designing Functional Programs (Advanced)
\item Competitive Prorgamming
\end{itemize}

\subsubsection*{Relevant Class Projects}
\begin{itemize}
\setlength\itemsep{0em}
\item Developed an interpreter for a subset of Racket in CS 146.
\item Wrote a role-playing game from scratch and developed art for it as a high school senior-year project.
\end{itemize}

\subsubsection*{Relevant Research Projects}
\begin{itemize}
\setlength\itemsep{0em}
\item Extended a C static analysis framework and a symbolic execution engine targetting LLVM bytecode. Demonstrated 17x speedup over previously published results for selected test cases by avoiding combinatorial explosion.
\item Developed and tested software for directional wireless localization, using ambient WiFi and a directional antenna to determine user's position and bearing.
\end{itemize}

\vspace{1em}

\begin{center}
\section*{Awards/Activities}
\end{center}

\subsubsection*{Debate Team}
\begin{itemize}
\setlength\itemsep{0em}
\item Held position of President.
\item Planned tournament schedule and handled registration.
\item Trained junior team members on basic debating skills.
\end{itemize}

\subsubsection*{Academic Awards}
\begin{itemize}
\setlength\itemsep{0em}
\item University of Waterloo President's Entrance Scholarship.
\item Singapore Science and Engineering Fair 2011 Gold Medal.
\item National Olympiad in Informatics 2011 Silver Medal.
\end{itemize}

\subsubsection*{Hackathons}
\begin{itemize}
\setlength\itemsep{0em}
\item Headlights - YHack 2014 second place. Helmet mounted Bicycle turn signals controlled by arm signals.
\item Myourtual Reality - BoilerMake 2014 Google Sponsor Prize. Control 3D objects in a augmented reality platform.
\item Eyedentify - HackMIT 2014 Qualcomm Sponsor Prize. Image and text recognition for Google Glass.
\end{itemize}

\subsection*{Side Projects}

\subsubsection*{Interactive SICP \hfill \href{http://xuanji.appspot.com/isicp/}{\tt xuanji.appspot.com/isicp/}}
\begin{itemize}
\setlength\itemsep{0em}
\item Interactive online version of the classic CS textbook Structure and Interpretation of Computer Programs where users can edit and run code fragments.
\item Project was voted to \#1 spot on Hacker News.
\end{itemize}

\subsubsection*{libgit2.js \hfill \href{https://github.com/zodiac/libgit2.js}{\tt github.com/zodiac/libgit2.js}}
\begin{itemize}
\setlength\itemsep{0em}
\item Javascript port of the libgit2 git library, compiled using Emscripten.
\item Includes commit tree and directory visualizer.
\end{itemize}

\end{document}
